Deep ordinal classification based on cumulative link models

### 2019-05-24 paper/ieee.tex
ggamma, inceptionresnetv2 functional api, paper

	\section{Introduction}
	\label{sect:introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly}. Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays. CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}. For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features. At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. However, the softmax may not be the best option depending on the problem considered.

@@

%		\textbf{(Binarización. Resolución de varios subproblemas.)}
	Z. Niu et al. \cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using CNNs. They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively solve these classification sub-problems, taking into account the correlation between them.

%		\textbf{(Binarización. Resolución de varios subproblemas.)}
	H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease as multiple binary sub-problems.

%		\textbf{(Binarización. Resolución de varios subproblemas.)}
	Y. Liu et al. \cite{liu2017deep} proposed a new approach which transforms the ordinal regression problem to binary classification sub-problems and use triplets with instances from different categories to train deep neural networks. In this way, high-level features describing the ordinal relationships are extracted automatically. Given that triplets must be generated, this approach is only recommended for small datasets.

%		\textbf{(Binarización. Resolución de varios subproblemas.)}
	S. Chen et al. \cite{chen2017using} proposed a deep learning method termed Ranking-CNN. This method combines multiple binary CNNs that are trained with ordinal age labels. The binary outputs are aggregated for the final age prediction. They achieved a tighter error bound for ranking-based age estimation.

@@

%		\textbf{(Función de coste ordinal)}
	J. de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm. They compared this cost function against the traditional log-loss function using three different datasets, including the Diabetic Retinopathy database as the most complex one. They proved that their function could improve the results as it reduces overfitting and training time. Also, they checked the importance of hyper-parameter tuning.

%		\textbf{(Funcion de coste ordinal)}
	A. Rios et al. \cite{rios2017ordinal} presented a CNN model designed to handle ordinal regression tasks on psychiatric notes. They combined an ordinal loss function, a CNN model and conventional feature engineering. Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.

%		\textbf{(Funcion de coste ordinal)}
	H. Fu et al. \cite{fu2018deep} applied deep learning techniques to Monocular Depth Estimation. They introduced a spacing-increasing discretization strategy to treat the problem as an ordinal regression problem. They improved the performance when training the network with an ordinal regression loss. Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.
%	\textcolor{red}{La parte ordinal no queda muy clara}

%		\textbf{(Funcion de coste ordinal)}
	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.

%		\textbf{(Multi-clase con restricciones)}
	Y. Liu et al. \cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes the negative loglikelihood for a multi-class problem constrained by the order relationship between instances.

@@

	%\textbf{(Función de coste ordinal y distribución unimodal.)}
	C. Beckham and C. Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions. The parameters of these distributions were learnt by using a deep neural network. They evaluated this approach on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results. They also included a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.

@@

%	The QWK metric is defined as follows:
%	\begin{equation}
%	\nonumber
%	\text{QWK} = 1 - \frac{\sum\limits^N_{i,j} \omega_{i,j} O_{i,j}}{\sum\limits^N_{i,j} \omega_{i,j} E_{i,j}},
%	\end{equation}
%	where $N$ is the number of samples rated, $\omega$ is the penalization matrix (in this case, quadratic weights are considered), $O$ is the confusion matrix, $E_{ij} = \frac{O_{i\bullet} O_{\bullet j}}{N}$, $O_{i\bullet}$ is the sum of the $i\text{-th}$ row and $O_{\bullet j}$ is the sum of the $j\text{-th}$ column.
%	
%	Then, they provided a continuous version of the QWK metric ($\text{QWK}_c$) based on the probabilities of the predictions:
%	\begin{equation}
%	\nonumber
%	\text{QWK}_c = 1 - \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q \left( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k)\right)},
%	\end{equation}
%	where $\text{QWK}_c \in [-1,1]$, $\mathbf{x}_k$ and $t_k$ are the input vector and the real class of the $k$-th sample, respectively, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ and $\omega_{i,j}$ are the elements of the penalization matrix. Generally, $\omega_{i,j} = \frac{|i-j|^n}{(C-1)^n}$, where $\omega_{i,j} \in [0,1]$.
%	
%	Then, they defined the loss function based on the QWK as follows:
%	\begin{equation}
%	\nonumber
%	\mathscr{L} = \log(1 - \text{QWK}_c),
%	\end{equation}
%	where $\mathscr{L} \in [-\infty, \log 2]$. $\mathscr{L}$ should be minimized, while the $\text{QWK}_c$ metric should be maximized.

%	\textcolor{red}{Yo intentaría organizar un poco el análisis que has hecho. Por ejemplo, podrías distinguir entre trabajos que modifican la función de error o los que modifican el modelo (ya sea aplicando binarización o utilizando distribuciones unimodales). o los que hacen las dos cosas. También habría que ir poniendo posibles pegas a cada artículo y destacar las ventajas de lo que proponemos (se impone una distribución unimodal, sin aplicar binarización, junco con una versión continua de una de las funciones d eerror más usadas)}

@@

%	\begin{table}[!t]
%		\caption{Description of the architecture used in the DR experiments.}
%		\label{table:CNNArchitecture}
%		\centering
%		\begin{tabular}{lc}
%			\hline
%			\hline
%			\textbf{Layer} & \textbf{Output shape}\\
%			\hline
%			2 x Conv3x3@32s1 & 252x252x32\\
%			MaxPool2x2s2 & 126x126x32\\
%			2 x Conv3x3@64s1 & 122x122x64\\
%			MaxPool2x2s2 & 61x61x64\\
%			2 x Conv3x3@128s1 & 57x57x128\\
%			MaxPool2x2s2 & 28x28x128\\
%			2 x Conv3x3@128s1 & 24x24x128\\
%			MaxPool2x2s2 & 12x12x128\\		
%			Conv4x4@128s1 & 9x9x128\\
%			\hline
%			\hline
%		\end{tabular}	
%	\end{table}
%	
%	\begin{table}[!t]
%		\caption{Description of the architecture used in the Adience experiments.}
%		\label{table:ResNetArchitecture}
%		\centering
%		\begin{tabular}{lc}
%			\hline
%			\hline
%			\textbf{Layer} & \textbf{Output shape}\\
%			\hline
%			Conv7x7@32s2 & 112x112x32\\
%			MaxPool3x3s2 & 55x55x32\\
%			2 x ResBlock3x3@64s1 & 55x55x32\\
%			1 x ResBlock3x3@128s2 & 28x28x64\\
%			2 x ResBlock3x3@128s1 & 28x28x64\\
%			1 x ResBlock3x3@256s2 & 14x14x128\\
%			2 x ResBlock3x3@256s1 & 14x14x128\\
%			1 x ResBlock3x3@512s2 & 7x7x256\\
%			2 x ResBlock3x3@512s1 & 7x7x256\\
%			AveragePool7x7s2 & 1x1x256\\
%			\hline
%			\hline
%		\end{tabular}	
%	\end{table}

@@

%	Fig. \ref{fig:lrdecay} represents the learning rate decay across $100$ epochs for the different initial values considered in this work.
%	\begin{figure}[!t]
%		\centering
%		\includegraphics[width=3in]{img/lr.pdf}
%		\caption{Representation of the learning rate decay.}
%		\label{fig:lrdecay}
%	\end{figure}

@@

%	\textcolor{red}{Es importante distinguir entre función de coste (usada para el ajuste de los pesos en el algoritmo de entrenamiento) y función de evaluación (usada para evaluar los modelos, en test o validación). Yo en esta parte describiría la de evaluación no la de coste, que debería estar descrita con el algoritmo, como hicimos en el congreso}
%	This evaluation measure gives a higher weight to the errors that are further from the correct class. A similar approach to the one described in \cite{de2018weighted} is used as the loss function as it gives better performance for ordinal classification problems. In this case, we define the QWK loss function ($\text{QWK}_c$) as follows:
%	\begin{equation}
%	\nonumber
%	\text{QWK}_c = \frac{\sum\limits_{k=1}^N \sum\limits_{q=1}^Q \omega_{t_k, q} P(y = \mathcal{C}_q | \mathbf{x}_k)}{\sum\limits_{i=1}^Q \frac{N_i}{N} \sum\limits_{j=1}^Q ( \omega_{i,j} \sum\limits_{k=1}^N P(y = \mathcal{C}_j | \mathbf{x}_k))},
%	\end{equation}
%	where $\text{QWK}_c \in [0,2]$, $\mathbf{x}_k$ and $t_k$ are the input data and the real class of the $k$-th sample, $Q$ is the number of classes, $N$ is the number of samples, $N_i$ is the number of samples of the $i$-th class, $P(y = \mathcal{C}_q | \mathbf{x}_k)$ is the probability that the $k$-th sample belongs to class $\mathcal{C}_q$ (estimated using the CLM structure), and $\omega_{i,j}$ are the elements of the penalization matrix. In this case, $\omega_{i,j} = \frac{(i-j)^2}{(C-1)^2}$, where $\omega_{i,j} \in [0,1]$.

@@

	Given that there exist significant differences between the means, we analyse now these differences. A post-hoc multiple comparison test has been performed on the mean QWK obtained. An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups. The results of this test over the test set are shown in Table \ref{table:Tukey}. They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it. Also, the best value for the LR parameter is $10^{-3}$. The BS is not relevant for this dataset with the values considered.
%		
%	\begin{table}[!t]
%		\caption{Tukey's test results for the DR dataset.}
%		\label{table:TukeyDR}
%		\centering
%		\begin{tabular}{cccc}
%			\hline\hline
%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
%			 \texttt{logit}   &  \texttt{probit}  &  $-0.002$  & $0.011$ \\
%			                  & \texttt{clog-log} &  $0.012$   & $0.000$ \\
%			 \texttt{probit}  &  \texttt{logit}   &  $0.002$   & $0.011$ \\
%			                  & \texttt{clog-log} &  $0.014$   & $0.248$ \\
%			\texttt{clog-log} &  \texttt{logit}   &  $-0.012$  & $0.000$ \\
%			                  &  \texttt{probit}  &  $-0.014$  & $0.248$ \\ \hline\hline
%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
%			    $10^{-2}$     &     $10^{-3}$     &  $-0.073$  & $0.000$ \\
%			                  &     $10^{-4}$     &  $-0.044$  & $0.000$ \\
%			    $10^{-3}$     &     $10^{-2}$     &  $0.073$   & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.029$   & $0.023$ \\
%			    $10^{-4}$     &     $10^{-2}$     &  $0.044$   & $0.000$ \\
%			                  &     $10^{-3}$     &  $-0.029$  & $0.023$ \\ \hline\hline
%		\end{tabular}
%	\end{table}

%	\begin{table}[!t]
%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
%		\label{table:ANOVAAdience}
%		\centering
%		\small
%		\begin{tabular}{lccccc}
%			\hline\hline
%			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
%			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
%			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
%			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
%			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
%			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
%			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
%			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
%			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
%			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
%			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
%			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
%		\end{tabular}
%	\end{table}
%	
	The results of the ANOVA III test for the Adience dataset, first, demonstrate that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$). Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).

@@

%	\begin{table}[!t]
%		\caption{Tukey's test results for the Adience dataset.}
%		\label{table:TukeyAdience}
%		\centering
%		\begin{tabular}{cccc}
%			\hline\hline
%			       LF         &        LF         & Mean diff. &  Sig.   \\ \hline
%			 \texttt{logit}   &  \texttt{probit}  &  $0.046$   & $0.000$ \\
%			                  & \texttt{clog-log} &  $0.084$   & $0.000$ \\
%			 \texttt{probit}  &  \texttt{logit}   &  $-0.046$  & $0.000$ \\
%			                  & \texttt{clog-log} &  $0.038$   & $0.000$ \\
%			\texttt{clog-log} &  \texttt{logit}   &  $-0.084$  & $0.000$ \\
%			                  &  \texttt{probit}  &  $-0.038$  & $0.000$ \\ \hline\hline
%			       LR         &        LR         & Mean diff. &  Sig.   \\ \hline
%			    $10^{-2}$     &     $10^{-3}$     &  $-0.046$  & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.148$   & $0.000$ \\
%			    $10^{-3}$     &     $10^{-2}$     &  $0.046$   & $0.000$ \\
%			                  &     $10^{-4}$     &  $0.194$   & $0.000$ \\
%			    $10^{-4}$     &     $10^{-2}$     &  $-0.148$  & $0.000$ \\
%			                  &     $10^{-3}$     &  $-0.194$  & $0.000$ \\ \hline\hline
%			       BS         &        BS         & Mean diff. &  Sig.   \\ \hline
%			       64         &        128        &  $-0.041$  & $0.026$ \\
%			                  &        256        &  $-0.027$  & $0.000$ \\
%			       128        &        64         &  $0.041$   & $0.026$ \\
%			                  &        256        &  $0.014$   & $0.000$ \\
%			       256        &        64         &  $0.027$   & $0.000$ \\
%			                  &        128        &  $-0.014$  & $0.000$ \\ \hline\hline
%		\end{tabular}
%	\end{table}

@@

%	\begin{table}[!t]
%		\caption{Comparison between the best results of nominal, ordinal and previous works for the DR dataset.}
%		\label{table:ComparisonDR}
%		\scriptsize
%		\centering
%		\def\arraystretch{1.3}
%		\begin{tabular}{lccc}
%			\hline
%			\hline
%			Method                                   & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
%			Ordinal network                          &    $0.582_{(0.016)}$    &    $0.723_{(0.004)}$    &        $0.868_{(0.002)}$         \\
%			Nominal network                          &    $0.498_{(0.013)}$    &    $0.692_{(0.014)}$    &        $0.854_{(0.006)}$         \\
%			J. Torre et al. \cite{de2018weighted}    &  $0.537_{(\text{-})}$   &            -            &                -                 \\
%			À. Nebot et al. \cite{nebot2016diabetic} &  $0.555_{(\text{-})}$   &            -            &                -					\\
%			\hline
%			\hline
%		\end{tabular}
%	\end{table}
%	
%	\begin{table}[!t]
%		\caption{Comparison between the best results of nominal, ordinal and previous works for the Adience dataset.}
%		\label{table:ComparisonAdience}
%		\scriptsize
%		\centering
%		\def\arraystretch{1.3}
%		\begin{tabular}{lccc}
%			\hline\hline
%			Method                                    & $\overline{QWK}_{(SD)}$ & $\overline{CCR}_{(SD)}$ & $\overline{\text{1-off}}_{(SD)}$ \\ \hline
%			Ordinal network                           &    $0.881_{(0.005)}$    &    $0.519_{(0.013)}$    &        $0.894_{(0.005)}$         \\
%			Nominal network                           &    $0.787_{(0.004)}$    &    $0.458_{(0.008)}$    &        $0.800_{(0.007)}$         \\
%			Beckham et al. \cite{beckham2017unimodal} &    $0.855_{(0.012)}$    &    $0.467_{(0.019)}$    &        $0.867_{(0.011)}$         \\
%			E. Eidinger et al. \cite{eidinger2014age} &            -            &    $0.451_{(0.026)}$    &        $0.807_{(0.011)}$         \\
%			J.-C. Chen et al. \cite{chen2016cascaded} &            -            &    $0.529_{(0.060)}$    &        $0.885_{(0.022)}$         \\
%			G. Levi et al. \cite{levi2015age}         &            -            &    $0.507_{(0.051)}$    &        $0.847_{(0.022)}$         \\ \hline\hline
%		\end{tabular}
%	\end{table}

>>>>

	\section{Introduction}
	\label{sect:introduction}
	% The very first letter is a 2 line initial drop letter followed
	% by the rest of the first word in caps.
	% 
	% form to use if the first word consists of a single letter:
	% \IEEEPARstart{A}{demo} file is ....
	% 
	% form to use if you need the single drop letter followed by
	% normal text (unknown if ever used by the IEEE):
	% \IEEEPARstart{A}{}demo file is ....
	% 
	% Some journals put the first two words in caps:
	% \IEEEPARstart{T}{his demo} file is ....
	% 
	% Here we have the typical use of a "T" for an initial drop letter
	% and "HIS" in caps to complete the first word.
	\IEEEPARstart{D}{eep learning}, introduced by Yann Lecun~\cite{lecun2015deep}, combines multiple machine learning techniques and allows computational models that are composed of numerous processing layers to learn representations of data with various levels of abstraction. These methods have dramatically improved the state-of-the-art in many domains, such as image classification~\cite{cirecsan2012multi,he2016deep,krizhevsky2012imagenet}, speech recognition~\cite{hinton2012deep}, control problems~\cite{mnih2015human}, object detection~\cite{jiang2016speed,girshick2014rich}, privacy and security protection~\cite{yu2017iprivacy,yuan2019adversarial,tan2018deep}, recovery of human pose~\cite{hong2015multimodal}, semantic segmentation~\cite{long2015fully} and image retrieval~\cite{li2015weakly,jin2018deep}. Convolutional Neural Networks (CNN) are one of the types of deep networks that are designed to process data that come in the form of multiple arrays. CNNs are appropriate for images, video, speech and audio processing, and they have been used extensively in the last years for automatic classification tasks~\cite{dong2014learning,sun2013deep,ronneberger2015u}. For images, each colour channel is represented by a 2D array, and convolutional layers extract the main features from the pixels, and, after that, a fully connected layer classify every sample based on its extracted features. At the output of the CNN, a softmax function provides the probabilities of the set of classes predefined in the model for classification tasks. However, the softmax may not be the best option depending on the problem considered.

@@

	Z. Niu et al. \cite{niu2016ordinal} proposed a learning approach to address ordinal regression problems using CNNs. They divided the problem into a series of binary classification sub-problems and proposed a multiple output CNN optimization algorithm to collectively solve these classification sub-problems, taking into account the correlation between them.

	H. Li et al. \cite{li2017deep} applied deep learning techniques for solving the ordinal problem of Alzheimer's diagnosis and detecting the different levels of the disease as multiple binary sub-problems.

	Y. Liu et al. \cite{liu2017deep} proposed a new approach which transforms the ordinal regression problem to binary classification sub-problems and use triplets with instances from different categories to train deep neural networks. In this way, high-level features describing the ordinal relationships are extracted automatically. Given that triplets must be generated, this approach is only recommended for small datasets.

	S. Chen et al. \cite{chen2017using} proposed a deep learning method termed Ranking-CNN. This method combines multiple binary CNNs that are trained with ordinal age labels. The binary outputs are aggregated for the final age prediction. They achieved a tighter error bound for ranking-based age estimation.

@@

	J. de la Torre et al.~\cite{de2018weighted} proposed the use of a continuous version of the quadratic weighted kappa (QWK) metric as loss function for the optimization algorithm. They compared this cost function against the traditional log-loss function using three different datasets, including the Diabetic Retinopathy database as the most complex one. They proved that their function could improve the results as it reduces overfitting and training time. Also, they checked the importance of hyper-parameter tuning.

	A. Rios et al. \cite{rios2017ordinal} presented a CNN model designed to handle ordinal regression tasks on psychiatric notes. They combined an ordinal loss function, a CNN model and conventional feature engineering. Also, they applied a technique called Locally Interpretable Model-agnostic Explanation (LIME) to make the non-linear model more interpretable.

	H. Fu et al. \cite{fu2018deep} applied deep learning techniques to Monocular Depth Estimation. They introduced a spacing-increasing discretization strategy to treat the problem as an ordinal regression problem. They improved the performance when training the network with an ordinal regression loss. Also, they used a multi-scale network structure that avoids unnecessary spatial pooling.

	A. Pal et al. \cite{pal2018severity} defined a loss function for CNN that is based on the Earth Mover's Distance and takes into account the ordinal class relationships.

	Y. Liu et al. \cite{liu2018constrained} proposed a constrained optimization formulation for the ordinal regression problem which minimizes the negative loglikelihood for a multi-class problem constrained by the order relationship between instances.

@@

	C. Beckham and C. Pal~\cite{beckham2017unimodal} proposed a straightforward technique to constrain discrete ordinal probability distributions to be unimodal, via the use of the Poisson and binomial probability distributions. The parameters of these distributions were learnt by using a deep neural network. They evaluated this approach on two large ordinal image datasets, including the Adience dataset used in this paper, obtaining promising results. They also included a simple squared-error reformulation \cite{beckham2016simple} that was sensitive to class ordering.

@@

@@

@@

@@

@@

	Given that there exist significant differences between the means, we analyse now these differences. A post-hoc multiple comparison test has been performed on the mean QWK obtained. An HSD Tukey's test \cite{tukey1949comparing} has been selected under the null hypothesis that the variance of the error of the dependent variable is the same between the groups. The results of this test over the test set are shown in Table \ref{table:Tukey}. They show that the best LF is the \texttt{clog-log} but the \texttt{probit} link performance is close to it. Also, the best value for the LR parameter is $10^{-3}$. The BS is not relevant for this dataset with the values considered.

	%	\begin{table}[!t]
	%		\caption{ANOVA III for the analysis of the main factors in the design of a Convolutional Ordinal Neural Network for the Adience dataset.}
	%		\label{table:ANOVAAdience}
	%		\centering
	%		\small
	%		\begin{tabular}{lccccc}
	%			\hline\hline
	%			            \multicolumn{6}{c}{Response variable QWK}             \\ \hline
	%			Source        &   S.S.   & D.F.  &  M.S.   &  F-ratio   &  Sig.   \\ \hline
	%			Model         & $84.372$ & $27$  & $3.125$ & $4414.006$ & $0.000$ \\
	%			$L$ factor    & $0.156$  &  $2$  & $0.078$ & $110.103$  & $0.000$ \\
	%			$P$ factor    & $0.925$  &  $2$  & $0.462$ & $653.163$  & $0.000$ \\
	%			$B$ factor    & $0.040$  &  $2$  & $0.020$ &  $28.218$  & $0.000$ \\
	%			$LP$ factors  & $0.284$  &  $4$  & $0.071$ & $100.118$  & $0.000$ \\
	%			$LB$ factors  & $0.008$  &  $4$  & $0.002$ &  $2.837$   & $0.028$ \\
	%			$PB$ factors  & $0.026$  &  $4$  & $0.007$ &  $9.267$   & $0.000$ \\
	%			$LPB$ factors & $0.021$  &  $8$  & $0.003$ &  $3.728$   & $0.001$ \\
	%			Error         & $0.076$  & $108$ & $0.001$ &            &  \\ \hline
	%			Total         & $84.449$ & $135$ &         &            &  \\ \hline\hline
	%		\end{tabular}
	%	\end{table}

	The results of the ANOVA III test for the Adience dataset, first, demonstrate that there exist significant differences in average QWK concerning the three factors ($\text{p-value} = 0.000$). Secondly, we found interactions between all the pairs of factors and between all the three factors together (p-values $0.000$, $0.000$, $0.000$ and $0.001$, respectively).

@@

@@
